---
title: "Owen et al. - Figure 3"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

This script will reproduce Figure 3 from *Owen et al. - Sample size planning for insect critical thermal limits studies*. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load required packages 

```{r packages, message = FALSE, warning = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, 
               tidyr,
               readr,
               data.table,
               viridis,
               here)
```

### Set ggplot theme (makes nice plots)

```{r plot_defaults, warning = FALSE}
theme_set(theme_classic() +
            theme(panel.border = element_rect(colour = "black", fill = NA),
                  axis.text = element_text(colour = "black"),
                  axis.title.x = element_text(margin = unit(c(2, 0, 0, 0), "mm")),
                  axis.title.y = element_text(margin = unit(c(0, 4, 0, 0), "mm")),
                  legend.position = "none"))
```

### Load bootstrap data 

We have already drawn our bootstrap samples, load that data. This is the output from script-01.

```{r load_data}
# Load raw data (with CI's)
boot_tci <- readr::read_csv(here::here("./data_clean/ct_min_bootstrap_with_ci.csv"))

# Make insect_sp column into a factor 
boot_tci <- boot_tci %>%
  dplyr::mutate(insect_sp = as.factor(insect_sp))
```

### Perform analysis

Here, we calculate the change in the width of the 95% confidence interval (CI) of the CTmin estimate for each species, and then average over all species in our dataset. 

```{r analysis, message = FALSE}
# Calculate change in width of CI, averaged across all species 
ci_width_change <- boot_tci %>%
  dplyr::mutate(
    # Calculate 95% CI width 
    w_ci = upper_ci - lower_ci,
    # Calculate the change in 95% CI width
    ci_change = abs(w_ci-lag(w_ci))) %>%
  # Summarise mean values across each species and sample size 
  dplyr::group_by(insect_sp, sample_size) %>%
  dplyr::summarise(
    # Calculate mean 95% CI change
    ci_change_mean = mean(ci_change, na.rm = TRUE),
    # Calculate standard deviation of 95% CI change
    ci_change_sd   = sd(w_ci, na.rm = TRUE),
    # Calculate standard error of 95% CI change
    ci_change_se   = ci_change_mean/sqrt(sample_size),
    # Calculate mean - 1 se of 95% CI change
    lower_se       = mean(ci_change_mean - ci_change_se),
    # Calculate mean + 1 se of 95% CI change
    upper_se       = mean(ci_change_mean + ci_change_se)) %>%
  # Keep a single row per insect_sp + sample_size 
  dplyr::slice(1) %>%
  dplyr::ungroup() %>%
  # Now average over all species
  dplyr::group_by(sample_size) %>%
  dplyr::summarise(ci_change_mean = mean(ci_change_mean),
                   lower_se       = mean(lower_se),
                   upper_se       = mean(upper_se))
```

### Make figure 

```{r fig3}
# Plot relationship - averaged across species (focused y axis)
ci_width_change %>%
  # Set mean and upper se upper limit to 2 for ease of visualisation 
  dplyr::mutate(upper_se = dplyr::if_else(upper_se > 2, 
                                          2, 
                                          upper_se)) %>%
  dplyr::mutate(ci_change_mean = dplyr::if_else(ci_change_mean > 2, 
                                          2, 
                                          ci_change_mean)) %>%
  # Remove n = 3 for visualisation (when mean > 2, R removes the entire line)
  dplyr::filter(sample_size > 3) %>%
  ggplot(data = ., aes(x = sample_size, 
                       y = ci_change_mean)) +
  geom_ribbon(aes(ymin = lower_se, 
                  ymax = upper_se),
              fill = "gray80") +
  geom_line() + 
  scale_y_continuous(breaks = seq(0, 2, 0.25), 
                     limits = c(0, 2)) +
  labs(x = "Sample size (n)",
       y = "Change in width of 95% CI (°C)") 

```

```{r save_figure}
# Save figure to file 
ggplot2::ggsave(here::here("./figures/ci_ctmin_ci_ci_width_all_species_focus.png"), 
                width = 6, 
                height = 6)
```

